\Large Ten Simple Rules for Scientific Fraud \& Misconduct

### 2017-06-28 article.tex
First complete draft with John Timmer

% Headers
\usepackage{fancyhdr}
\pagestyle{fancy}
% \fancyhf{}
\rhead{\footnotesize \sf \today}
\lhead{\footnotesize \sf NP Rougier \textbullet~Ten Simple Rules for Fraud \& Misconduct}
\rfoot{\footnotesize \sf \thepage}
\cfoot{}
\lfoot{}

@@

\title{Ten Simple Rules for Fraud \& Misconduct}
\author{%
  \textbf{Nicolas P. Rougier}$^{1,2,3,*}$\\
  \begin{footnotesize}
    $^{1}$INRIA Bordeaux Sud-Ouest
          Talence, France
    $^{2}$Institut des Maladies Neurodégénératives,
          Université de Bordeaux, CNRS UMR 5293,
          Bordeaux, France
    $^{3}$LaBRI, Université de Bordeaux, Institut Polytechnique de Bordeaux,
          CNRS, UMR 5800, Talence, France\\
    $^{*}$Corresponding author:
          \href{mailto:Nicolas.Rougier@inria.fr}{Nicolas.Rougier@inria.fr}
  \end{footnotesize}
}

@@

\begin{tcolorbox}[breakable, pad at break*=1mm,
    colback=yellow!5, arc=0pt, outer arc=0pt, boxrule=0pt, frame hidden]
\begin{small}
\noindent {\sf \textbf{Disclaimer.} We do not encourage scientific fraud nor
  misconduct. The goal of this provocative article is to alert the reader on a
  preoccupying situation in Science. Facing the Publish or Perish alternative,
  a number of researchers have decided to cross the Rubicon without the full
  knowledge of the dramatic consequences that may hurt Science and impact not
  only their scientific life but their actual life as well. If you're tempted
  to (even so slightly) beautify your results, keep in mind that the game is
  probably not worth the risks.}\par
\end{small}
\end{tcolorbox}

@@

So, here we are! You've decided to join the dark side of Science. That's great!
You'll soon discover a brand new world of shiny and surprising results,
non-replicable experiments, fabricated data, funny statistics, fame and shame,
joy and sadness, and... jail. But you've made your choice (for whatever
reasons) and you better have to be well prepared because Science is strong on
the other side. Only a few years from now, fraud and misconduct was a piece of
cake (\href{https://en.wikipedia.org/wiki/The_Turk}{Mechanical Turk},
\href{https://en.wikipedia.org/wiki/Charles_Redheffer}{Perpetual motion
  machine}, \href{https://en.wikipedia.org/wiki/Great_Moon_Hoax}{Life on Moon},
\href{https://en.wikipedia.org/wiki/Piltdown_Man}{Piltdown man},
\href{https://en.wikipedia.org/wiki/Water_memory}{Water memory}). Problem is
that there are new players in town (\href{https://pubpeer.com}{PubPeer},
\href{http://retractionwatch.com}{RetractionWatch},
\href{https://forbetterscience.com}{For Better Science},
\href{http://blogs.discovermagazine.com/neuroskeptic/}{Neuroskeptic} to name
just a few) and they're pretty good at spotting and reporting fraudsters.
Furthermore, publishers have started to retaliate with high-tech tools. To
commit fraud or misconduct without getting caught in 2017 is kind of a
challenge and requires a real dedication to your task. But there will be always
people that think they're smarter than a whole community. And because we love
to have things done in the proper way, we're kind enough to give you some
simple rules to follow in your brand new career (see also \citep{timmer:2012}
for a set of complementary rules). However, results and consequences are not
guaranteed.

\section*{Rule 1: Misrepresent, falsify or fabricate your data}

In order to start a plain and deceitful scientific fraudster life, the very
first thing you need to gain expertise on is to learn how to convincingly
misrepresent, falsify or fabricate your data. If you're still hesitating at
embracing the dark side of Science, you may start with a slight
mis-representation to strengthen your hypothesis. Some classical techniques are
illustrated in the seventh rule of \citep{rougier:2014} but there are
actually \href{https://en.wikipedia.org/wiki/Misleading_graph}{many more
  techniques} to make a graph misleading \citep{wainer:1984,raschke:2008}. You
can also directly change your results in a post-production phase by using
software such as Photoshop or Gimp that makes it really easy to change pretty
much anything in a figure \citep{cromey:2012, hendricks:2011}. But be careful
of not making too obvious manipulations because an ever-growing number of
journals are now equipped with forensic software to spot image manipulation
\citep{white:2007, rossner:2004,hsu:2015} (see also
\href{http://journals.plos.org/ploscompbiol/s/figures#loc-image-manipulation}{PLoS
  image manipulation recommendation}). You can even test your image online
using \href{https://29a.ch/photo-forensics/#forensic-magnifier}{Forensically}
by Jonas Wagner. This should dissuade you from manipulating your image by
yourself.
%
%% \begin{wrapfigure}{r}{0.4\textwidth}
%% %  \vspace{-8mm}
%%   \begin{center}
%%     \includegraphics[width=0.4\textwidth]{datasaurus}
%%   \end{center}
%%   \caption{The Datasaurus set by \href{http://www.thefunctionalart.com/2016/08/download-datasaurus-never-trust-summary.html}{Alberto Cairo}. }
%%   \label{fig:datasaurus}
%% \end{wrapfigure}
%
Furthermore, none of the previous techniques will change the statistics of your
data and it might a better choice to falsify your data. Starting with real
data, you can change only a few points in order to change a non-significant
results into an astoundingly highly significant result as shown on the
\href{http://shinyapps.org/apps/p-hacker/}{p-hacker} application
\citep{schonbrodt:2015} or the interactive applet from
\citep{aschwanden:2015}. The advantage of falsifying real data is that changing
only a few points will still make your data looks good and not too much
suspicious. The disadvantage is that it requires some real data in the first
place and thus it requires to carry on some actual experiment (i.e. some
work). As a last resort, you can also fabricate the whole data set using a
specific program. For example, starting from a given X mean/SD, Y mean/SD, and
a correlation coefficient, you can generate a data set with these precise
statistics \citep{matejka:2017}. Do not pick the datasaurus set because if you
plot it, it might look suspicious for the alert reader. Finally, make sure to
have a backup story when people will start asking or investigating
how/when/where/how did you do perform the experiments to get these data. A
number of misconducts have been detected after just a few questions
\citep{vastag:2006}.

@@

%% \begin{wrapfigure}{l}{0.4\textwidth}
%%   \vspace{-5mm}
%%   \begin{center}
%%     \includegraphics[width=0.4\textwidth]{xkcd}
%%   \end{center}
%%   \caption{P-Values by XKCD (\url{https://xkcd.com/1478/}). This work is
%%     licensed under a CC-BY-NC 2.5 License.}
%%   \label{fig:xkcd}
%% \end{wrapfigure}
If you are reluctant at manipulating your data, you still have the option of
simply hacking your results in order to reach the significance level
(a.k.a. p-hacking). But before committing any scientific misconduct, are you
sure you need to do so? What is the p value of your NHST (Null Hypothesis
Significance Test)? Did you consider using one of the many qualification
proposed by
\href{https://mchankins.wordpress.com/2013/04/21/still-not-significant-2/}{Matthew
  Hankins} to report your results? Can't you use expression such as {\em nearly
  acceptable level of significance (p=0.06)}, {\em very closely brushed the
  limit of statistical significance (p=0.051)} or {\em weakly statistically
  significant (p=0.0557)}? It does not make sense, but in some cases, it might
be sufficient to convince a naive reviewer or reader. However, if you're
suffering from a bi-polar p-value disorder (term coined by
\href{http://daniellakens.blogspot.fr/2014/05/the-probability-of-p-values-as-function.html}{Daniel
  Lakens}), you'll want to reach the magical 0.05 threshold and it might
actually be much easier than you think because the correct usage of the
infamous p-value is hardly understood by a number of students, teachers or
researchers \citep{haller:2002,lecoutre:2003}. The current situation is
actually so bad that the American Statistical Association had to release a
statement to explain the correct usage \citep{wasserstein:2016,} last year and
Nature has issued as well some warning on the usage of the p-value
\citep{baker:2016}. Consequently, before hacking your results, it might be wise
to re-read your classics
\citep{simmons:2011,cumming:2012a,cumming:2012b,colquhoun:2014} if you want to
take full advantage of the misuse of p-value. Last, but not least, if you're in
psychology, you have to take extra-precaution because this domain has recently
raised concerns, especially when it comes to the unusual distribution of
p-values smaller than 0.05 \citep{hartgerink:2016,bakker:2012}. If you add the
statcheck variable into the equation \citep{nuijten:2015,epskamp:2016}, it
might be difficult to achieve a proper p-hacking of your results without being
noticed. Even though some people would call such results checking {\em
  methodological terrorism} \citep{finske:2016}, it might be time to reconsider
your commitment to the dark side of Science.

@@

You have your (fake) results but you still need to publish your clickbait
article to gain fame (and tenure and professorship). Writing is a tedious task
and might represent a fair amount of work. Writing the state of the art in your
domain requires to actually read (what?) what your colleagues have been doing
over the past few years. It is a very time consuming task. But if one of these
colleagues wrote a nice introduction to the domain or a wonderful state of the
art, why bother writing a new one? Why not copy/paste what he/she has written
instead?  Plagiarism is the nuts and bolts of scientific misconduct
\citep{neuroskeptic:2017}, be it literal copying, substantial copying or
paraphrasing (see
\href{https://www.elsevier.com/editors/perk/plagiarism-complaints}{definitions
  from Elsevier} and the committee on publication ethics (COPE) procedure to
handle plagiarism in a
\href{https://www.elsevier.com/__data/assets/pdf_file/0005/72815/plagiarism-A.pdf}{submitted}
or
\href{https://www.elsevier.com/__data/assets/pdf_file/0020/72830/plagiarism-B_0.pdf}{published}
article). Of course, you cannot literally copy paste an excerpt of text from an
article to insert it in yours. Just imagine a situation where the reviewer
would also be the author of the text being reviewed. Consequently, if you
really intend to plagiarize, you'll need to transform the text drastically to
avoid detection by humans \citep{dorigo:2015,} and more importantly, to avoid
detection by dedicated software (e.g. iThenticate). These software are used by
universities and journals for tracking people just like you. And since their
database is really huge, plagiarism is harder and harder. Can you imagine than
self-plagiarism is not even allowed for a vast majority of journals? In the
end, you really have to improve or innovate in your techniques and to work very
hard \citep{long:2009}. But faced with such an adversarial nature of the
situation, to write your very own text might be an easier option.

@@

%% \begin{wrapfigure}{r}{0.5\textwidth}
%%   \vspace{-5mm}
%%   \begin{center}
%%     \includegraphics[width=0.5\textwidth]{phd-comics}
%%   \end{center}
%%   \caption{Addressing reviewers comments. PhD Comics
%%     (\url{http://phdcomics.com}). Copyright (c) 2005 Jorge Cham.}
%% \end{wrapfigure}

Results and papers are ready and it is now time to submit. Depending on the
journal you target, you may still encounter some problem with the review
process. If reviewers are a bit too picky, they may ask you annoying questions,
be a bit suspicious, request more information, ask for a major revision and or
even reject your submission (can you imagine?). After all your hard work at
fabricating the data and plagiarized the article, that would be really
unfair. Fortunately, there is a simple solution. You can actually write your
own review! How is that possible you may ask? It is incredibly easy. At the
time of submission, you will be asked to give name of possible reviewers, just
give phony names with corresponding email addresses that will be redirected to
your mailbox. You will soon receive an invitation to review and you're then
free to write your own review and state how brilliant is your own work. Of
course, you'll have to write a review that looks like an actual review. If
you're Machiavellian, you will have introduced some factual errors in your
manuscript such that you can report them later in your review. Make sure also
to not send you review before the editor deadline because as
\href{https://arstechnica.com/science/2017/04/107-cancer-papers-retracted-due-to-peer-review-fraud/}{reported
  by Elizabeth Wager} \citep{stigbrand:2017}, one of the reasons the editors
spotted fake reviews was that reviewers responded just in time. However, editors and
publishers are now well aware of the scam \citep{ferguson:2014} and they have
taken counter-measures \citep{haug:2015}. For example, some of them do not offer
anymore the option to recommend unknown reviewer or if they do, the
recommendation is restricted to a list of certified reviewers. If you insist on
writing your own peer-review, you'll have to be creative and find new ways to
game the system.

@@

If most journals will most likely reject your submission because you've applied
some of the rules above and get caught red-handed, you still have opportunities
to publish your results in one of the many predatory publishers available on
the internet and the internet only \citep{shen:2015}. Such predators will
publish just anything
(\href{https://en.wikipedia.org/wiki/International_Journal_of_Advanced_Computer_Technology#Publication_controversy}{``Get
  Me Off Your Fucking Mailing List''} in the International Journal of Advanced
Computer Technology (2005, 2014)) and you have a 100\% chance to have your
article published with a lighting fast review, less than 24h for some
journals. Finding a predatory publisher used to be easy thanks to the list
created and maintained by Jeffrey Beal. Even if some people (and publishers)
have judged this list to be controversial, it was incredibly useful for a lot
of people. Unfortunately, this list has closed just a few months ago
\citep{straumsheim:2017} and the
soon-to-be released replacement one will not be free \citep{silver:2017}. But
you can now take advantage of the
\href{http://thinkchecksubmit.org}{Think/Check/Submit} website that provides a
easy-to-use checklist that researchers can refer to when they are investigating
whether a journal can be trusted. Just take the opposite of their wise
recommendations and make sure to \textbf{not} pick a journal from the list
\href{https://oaspa.org}{Open Access Scholarly Publishers Association} since
these journals have been thoroughly reviewed and can be trusted. For example,
if none of your colleagues know the journal, if the editorial board is made of
unknown or non-existent people \citep{sorokowski:2017} or even dogs in some
cases \citep{kennedy:2017} and no address / email / telephone is provided to
contact the publisher, you may have knocked at the right door. Of course, you
will have to pay exorbitant fees to have your work published, but this is the
price to pay to have an expedited and complaisant review, if any review at
all. Before making you decision where to publish, make sure to check as well
for the retraction fees that may be much higher than the initial publishing
fees in some cases. But who wants to retract anyway?

@@

%% \begin{wrapfigure}{l}{0.4\textwidth}
%%   \vspace{-6mm}
%%   \begin{center}
%%     \includegraphics[width=0.4\textwidth]{data-share}
%%   \end{center}
%%   \caption{Image by Ainsley Seago.}
%%   \label{fig:datasaurus}
%% \end{wrapfigure}

You managed to have your article published, congratulations! You'll probably
get a lot of buzz and maybe your amazing conclusion will make it to the
newspaper headlines if your research is sexy enough. Because of the buzz,
chances are increased that people will start asking you to access your
material, if the publisher has not already requested it prior to
publication. Of course, that's quite a bad news for you because if your data
has been fabricated or if your statistical analysis is not really academic,
your colleagues might discover your misconduct. Consequently, you definitely
cannot give access to your raw material. For this, you can use the same old
reasons that have prevented data sharing for a very long time
\citep{roche:2014}: ``Oh you know, my data cannot be anonymized'', ``No, you
would not understand the structure of my data'', ``A lot of money has been
invested, I cannot give it for free'', etc. You can also tell these people
asking for your data that they are {\em research parasites} \citep{longo:2016}
even though the techniques seems to have backfired since then
(\url{http://researchparasite.com}).  Technological excuses might also be worth
a try. When \citep{collberg:2014,collberg:2015} tried to access the code of
several publications, they get some really great answers ``Too busy to help'',
``Code will be available soon'', ``Bad backup practice'', etc. Just pick one
you like. Finally, with the increasing pressure by institutions (NIH, NSF,
Europe, etc) to share data, you can pretend (and only pretend) to be a
supporter of Open Data by inserting a simple ``data available upon request'' or
``data is available from my website''. This does not correspond at all to the
FAIR principles (findable, accessible, inter-operable, re-usable,
\cite{wilkinson:2016}), but who cares if you can give the illusion to not be
afraid of sharing your data? But don't get me wrong, you will never answer a
request, and the data will never appear on your website.

@@

Here comes the tricky part: replications. Can you imagine that some researchers
are willing to replicate your results based on what you've explained in your
article? \citep{nosek:2015} replicated 100 experiments reported in papers
published in three high-ranking psychology journal. And of course, they
concluded that some experiments were not replicable at all. How surprising!
Even worse, there is now scientific journals dedicated to replications
(e.g. \url{http://rescience.github.io}). If people start to replicate your work
and do not get the same results, you have a problem. You might be suspected of
fraud or misconduct and people will really insist on seeing you actual
data. You can try rule 6, but after several failed replication, it will be much
harder to deny access to your data. One easy way to avoid imminent disaster is
to claim beforehand in your article that the experiment/study has been already
replicated in your lab. The subliminal message to the reader is ``Don't bother
to replicate, we've already taken care of that and it works, believe us. Don't
lose your time, you will thank us later''. If this doesn't work, you can also
try a {\em Do Not Replicate order} as proposed by
\href{https://mchankins.wordpress.com/2014/07/12/do-not-replicate/}{Matthew
  Hankins} (who is kind enough as to provide a template). It is not yet widely
used yet, but with the replication crisis we're facing in several scientific
domain, we're confident it will soon become popular.

@@

If you've made a genuine (and big) mistake in your work, there is no problem in
asking for the retraction of your paper \citep{miller:2006}. This is actually a
behavior that is rewarded according to \citep{lu:2013}, even though in some
cases, it can take several years \citep{trivers:2009}. However, if you've been
frauding, having your paper retracted is like an admission of fraud and you
want to avoid that. Such retraction may start with a simple comment to the
editor saying there may be some problem with you paper. If you're lucky, such
comment, even if sound, will never make it into the journal
\citep{trebino:2009}, else, you'll have to give a convincing answer. Depending
how you addressed the comment, the editor can decide to retract your paper even
without your consent. Before reaching this failure climax, you better have to
start with a simple corrigendum pretexting a bad preparation of the material
for the publication.  Don't hesitate to publish as many corrigendum as
necessary to make critics happy. This can last for several years, the time
needed for people to forget about your fraud or misconduct.

@@

If you look at the yearly list of
\href{http://www.the-scientist.com/?articles.view/articleNo/47813/title/Top-10-Retractions-of-2016/}{top
  ten retractions} compiled by Adam Marcus and Ivan Oransky (co-founders of the
RetractionWatch) since 2012, you'll realize that all the above rules are
already quite well known in the community. If you want to stay off the radar
while committing fraud and misconduct, you'll have to be creative and invent
new rules.

>>>>

% Headers
\usepackage{fancyhdr}
\pagestyle{fancy}
% \fancyhf{}
\rhead{\footnotesize \sf \today}
\lhead{\footnotesize \sf Rougier \& Timmer \textbullet~Ten Simple Rules for Scientific Fraud \& Misconduct}
\rfoot{\footnotesize \sf \thepage}
\cfoot{}
\lfoot{}

@@

\title{\Large Ten Simple Rules for Scientific Fraud \& Misconduct}
\author{%
  \textbf{Nicolas P. Rougier}$^{1,2,3,*}$ \textbf{and John Timmer}$^{4}$\\
  \begin{footnotesize}
    $^{1}$INRIA Bordeaux Sud-Ouest
          Talence, France
    $^{2}$Institut des Maladies Neurodégénératives,
          Université de Bordeaux, CNRS UMR 5293,
          Bordeaux, France
    $^{3}$LaBRI, Université de Bordeaux, Institut Polytechnique de Bordeaux,
          CNRS, UMR 5800, Talence, France
    $^{4}$Ars Technica, Condé Nast, New York, NY, USA\\
    $^{*}$Corresponding author:
          \href{mailto:Nicolas.Rougier@inria.fr}{Nicolas.Rougier@inria.fr}
  \end{footnotesize}
}

@@

\begin{tcolorbox}[breakable, pad at break*=1mm,
    colback=yellow!5, arc=0pt, outer arc=0pt, boxrule=0pt, frame hidden]
\begin{small}
  \noindent {\sf \textbf{Disclaimer.} We obviously do not encourage scientific
    fraud nor misconduct. The goal of this article is to alert the reader to
    problems that have arisen in part due to the Publish or Perish imperative,
    which has driven a number of researchers to cross the Rubicon without the
    full appreciation of the consequences. Choosing fraud will hurt science,
    end careers, and could have impacts on life outside of the lab. If you're
    tempted (even slightly) to beautify your results, keep in mind that the
    benefits are probably not worth the risks.}\par
\end{small}
\end{tcolorbox}

@@

So, here we are! You've decided to join the dark side of Science. That's great!
You'll soon discover a brand new world of surprising results,
non-replicable experiments, fabricated data, and funny statistics. But it's not without risks: fame and shame,
retractions and lost grants, and... possibly jail. But you've made your choice, so now you need to know how to manage these risks. Only a few years ago, fraud and misconduct was a piece of
cake (See the \href{https://en.wikipedia.org/wiki/The_Turk}{Mechanical Turk},
\href{https://en.wikipedia.org/wiki/Charles_Redheffer}{Perpetual motion
  machine}, \href{https://en.wikipedia.org/wiki/Great_Moon_Hoax}{Life on Moon},
\href{https://en.wikipedia.org/wiki/Piltdown_Man}{Piltdown man},
\href{https://en.wikipedia.org/wiki/Water_memory}{Water memory}). But there are lots of new players in town (\href{https://pubpeer.com}{PubPeer},
\href{http://retractionwatch.com}{RetractionWatch},
\href{https://forbetterscience.com}{For Better Science},
\href{http://blogs.discovermagazine.com/neuroskeptic/}{Neuroskeptic} to name
just a few) who have gotten pretty good at spotting and reporting fraudsters.
Furthermore, publishers have started to arm themselves with high-tech tools, and your fellow scientists are willing to name and shame you \href{https://www.youtube.com/watch?v=FXaOqwanWnU/}{on social media}. To
commit fraud or misconduct without getting caught in 2017 is a real
challenge and requires serious dedication to your task. While you'll never be smarter than an entire community of scientists, we're generously giving you some
simple rules to follow in your brand new career in fraud (see also \citep{timmer:2012}
for a set of complementary rules). Of course, neither results or (lack of) consequences are 
guaranteed.

\section*{Rule 1: Misrepresent, falsify, or fabricate your data}

In order to start your life as a scientific fraudster, the
first thing you need to do is learn how to convincingly
misrepresent, falsify, or fabricate data. If you're still hesitant about
embracing the dark side of science, you can start with a slight
misrepresentation to support your hypothesis --- a hypothesis you're sure is right anyway. Some classic techniques are
described in more detail below (see the seventh rule of \citep{rougier:2014}) but there are a number of others. If your data include numbers, there are \href{https://en.wikipedia.org/wiki/Misleading_graph}{many
  techniques} for making a graph misleading \citep{wainer:1984,raschke:2008}. If you have images, you
can change your results using
software such as Photoshop or GIMP, which allow you to change pretty
much anything in a figure \citep{cromey:2012, hendricks:2011}. But be careful, as an ever-growing number of
journals are now using forensic software to spot image manipulation
\citep{white:2007, rossner:2004,hsu:2015} (see also
\href{http://journals.plos.org/ploscompbiol/s/figures#loc-image-manipulation}{PLoS
  image manipulation recommendation} and \href{http://jcb.rupress.org/content/166/1/11}{Rockefeller University Press' discussion of the issue}). You can even test your whether your image has issues that could tip off an editor using the online tool \href{https://29a.ch/photo-forensics/#forensic-magnifier}{Forensically}
by Jonas Wagner. This might dissuade you from manipulating your image, but don't worry --- there are plenty of other options available to you.\\

None of the previous techniques will change the statistics of your
data, so it might be good to consider your options here. Starting with real
data, you only need to change a few points in order to take a non-significant
result and turn it into something with an astoundingly highly significance. Just see what's possible using the
\href{http://shinyapps.org/apps/p-hacker/}{p-hacker} application
\citep{schonbrodt:2015} or the interactive applet from
\citep{aschwanden:2015}. The advantage of tweaking real data is that the results  look both good and not very
suspicious. The disadvantage is that it requires some real data in the first
place, which means carrying out some actual experiments. Who wants that? Instead, you can fabricate an entire data set using software. With just a little programming skill, you can choose a correlation coefficient and X and Y mean/SD, and generate a data set with these precise
statistics \citep{matejka:2017}. (Do not pick one of the datasaurus sets because if you
plot it, it might attract the attention of an alert reader.) Whatever option you choose, make sure to
have a backup story in case people start asking about the details of the experiments. A
number of misconduct cases have been detected with just a few questions
\citep{vastag:2006}.

@@

If you are reluctant to manipulate your data, you still have the option of
searching through your results to find anything that reaches significance 
(a.k.a. p-hacking). This can provide an appealing alternative to scientific misconduct. What is the p value of your NHST (Null Hypothesis
Significance Test)? If it's close to your field's standard one of the many qualification
proposed by
\href{https://mchankins.wordpress.com/2013/04/21/still-not-significant-2/}{Matthew
  Hankins} to report your results? Can't you use expression such as {\em nearly
  acceptable level of significance (p=0.06)}, {\em very closely brushed the
  limit of statistical significance (p=0.051)} or {\em weakly statistically
  significant (p=0.0557)}? While these statements don't make much sense, they might
be sufficient to convince a naive reviewer or reader.

If you're
suffering from a bi-polar p-value disorder, however (a term coined by
\href{http://daniellakens.blogspot.fr/2014/05/the-probability-of-p-values-as-function.html}{Daniel
  Lakens}), you'll want to reach the magical 0.05 threshold. It might be much easier than you think to portray your data as significant! The correct method for calculating the
infamous p-value is barely understood by many students, teachers, and
researchers \citep{haller:2002,lecoutre:2003}. The current situation is so bad that the American Statistical Association had to release a
statement to explain p's correct usage \citep{wasserstein:2016,};
Nature has issued a warning as well
\citep{baker:2016}. Consequently, before hacking your results, it might be wise
to re-read your classics
\citep{simmons:2011,cumming:2012a,cumming:2012b,colquhoun:2014}. A warning for those of you in psychology: you have to take extra-precaution because this field has drawn attention for the unusual distribution of
p-values smaller than 0.05 \citep{hartgerink:2016,bakker:2012}. There's now software called statcheck that can be used to recalculate the p values in your paper \citep{nuijten:2015,epskamp:2016}, making it difficult to get away with misleading statistics. Although some have called checking the results of others {\em
  methodological terrorism} \citep{finske:2016}, it might be enough to scare some away from the dark side of Science.

@@

It's not enough to have (fake) results; you still need to publish them if you want to gain fame (and tenure, and grants). Writing is a tedious task
and can be a fair amount of work. Summarizing the state of the art in your
field will force you to actually read about what your colleagues have been doing
over the past few years. It is a very time consuming task. But in doing that reading, you may find that one of these
colleagues wrote a nice introduction to the field or a wonderful summary of its current state. If so, why bother writing a new one? It's much simpler to copy/paste what he/she has written.  Plagiarism is the nuts and bolts of scientific misconduct
\citep{neuroskeptic:2017}, be it literal copying, substantial copying or
paraphrasing (see
\href{https://www.elsevier.com/editors/perk/plagiarism-complaints}{definitions
  from Elsevier} and the committee on publication ethics' (COPE) procedure for
handle plagiarism in a
\href{https://www.elsevier.com/__data/assets/pdf_file/0005/72815/plagiarism-A.pdf}{submitted}
or
\href{https://www.elsevier.com/__data/assets/pdf_file/0020/72830/plagiarism-B_0.pdf}{published}
article).

Of course, you cannot literally take an excerpt from an
article to insert it in yours. You'd run the risk of creating a situation where the reviewer found his own text in yours. Consequently, if you
really intend to plagiarize, you'll need to transform the text drastically to
avoid detection by humans \citep{dorigo:2015,} and more importantly, to avoid
detection by dedicated software (e.g. iThenticate). This software is used by
universities and journals for tracking people just like you. As the databases behind these services grow, plagiarism is becoming harder and harder. Even
self-plagiarism is not allowed by a vast majority of scientific journals. All of this means that you have to be really innovative in your plagiarism techniques \citep{long:2009}. We've reached the point where writing your own text might be an easier option.

@@

Even if you avoid all the pitfalls discussed above, you're in the clear yet. Depending on the
journal you target, you may still encounter problems with the review
process. If reviewers are picky, they may ask annoying questions,
request more information or experiments, ask for a major revision and/or reject your submission entirely. Can you imagine how this would make you feel after all your hard work
fabricating the data and plagiarized the article? There's even the risk that they'll notice your malpractice. Fortunately, there is a simple solution: write your
own review!

It is surprisingly easy to do. As you submit, you will often be asked to give name of possible reviewers. Just
provide phony names, along with email addresses that will be redirected to
your mailbox. You will soon receive an invitation to review your own work, and you're then
free to state how brilliant your own work is. Of
course, you'll have to write a review that looks like an actual review. If
you're Machiavellian, you can introduce some factual errors in your
manuscript, then report them in your review, making it look thorough. Make sure not to send you review before the deadline because as
\href{https://arstechnica.com/science/2017/04/107-cancer-papers-retracted-due-to-peer-review-fraud/}{reported
  by Elizabeth Wager} \citep{stigbrand:2017}, editors have
spotted fake reviews in part because reviewers responded promptly. Unfortunately, editors and
publishers are now aware of the scam \citep{ferguson:2014} and  have
taken counter-measures \citep{haug:2015}. For example, some of them no longer offer authors the option of recommending reviewers or if they do, the
recommendation is restricted to a list of certified reviewers. If you insist on
writing your own peer-review, you'll have to be creative and find new ways to
game the system.

@@

If you're worried that peer review will reveal your misconduct, you still have opportunities for publishing your results. There are many predatory publishers on
the internet \citep{shen:2015}. These predators will
publish just anything
(see \href{https://en.wikipedia.org/wiki/International_Journal_of_Advanced_Computer_Technology#Publication_controversy}{``Get
  Me Off Your Fucking Mailing List''} in the International Journal of Advanced
Computer Technology (2005, 2014)) and you have a 100\% chance of publication with a lighting fast review - less than 24h for some
journals. Finding a predatory publisher used to be easy thanks to a list
created and maintained by Jeffrey Beal. Although not all researchers (and publishers)
agreed with his categorization, this list provided an incredibly useful resource. Unfortunately, Beal's list was shut down just a few months ago
\citep{straumsheim:2017} and the
soon-to-be released replacement one will not be free \citep{silver:2017}. Still,
you can take advantage of the
\href{http://thinkchecksubmit.org}{Think/Check/Submit} website, which provides a
easy-to-use checklist that researchers can refer to when they are investigating
whether a journal is trustworthy. You'll obviously just want take the opposite of their sage recommendations --- like making sure \textbf{not} to pick a journal from the list of the 
\href{https://oaspa.org}{Open Access Scholarly Publishers Association} since
these journals have been thoroughly reviewed and can be trusted. Other anti-tips include finding a journal that none of your colleagues know about, looking for an editorial board that's made of
unknown or non-existent people \citep{sorokowski:2017} or dogs \citep{kennedy:2017}, and finding a publisher without any address / email / telephone number. Of course, you
will have to pay exorbitant fees to have your work published, but this is the
price to pay to have an expedited and complacent review, assuming there's any review at
all. Before making you decision where to publish, make sure to check
for the retraction fees, which may be much higher than the initial publishing
fees in some cases. But who wants to retract anyway?

@@

You managed to have your article published, congratulations! You'll probably
feel a bit of a buzz, and your astonishing conclusion may draw some
newspaper headlines if your research is sexy enough. Don't get too excited about this, though. Attention means an increased chance that other researchers will start asking to access your
material, assuming the publisher has not already requested it prior to
publication. Of course, that's very bad news for you if your data
has been fabricated or if your statistical analysis is not really academic. You definitely cannot give others access to your raw if it doesn't exist! Fortunately, researchers have been avoiding sharing their data for decades, and the same old
reasons still apply
\citep{roche:2014}: ``Oh you know, my data cannot be anonymized''; ``You
would not understand the structure of my data''; ``A lot of money has been
invested, I cannot give it for free''; etc. You can even tell anyone
asking for your data that they are {\em a research parasite} \citep{longo:2016}
although that approach seems to have drawn some unwanted attention
(\url{http://researchparasite.com}).  Technological excuses might also be worth
a try. When \citep{collberg:2014,collberg:2015} tried to access the code used in
several publications, they get some really great answers: ``Too busy to help'';
``Code will be available soon''; ``Bad backup practice''; etc. Just pick one
you like. With the increasing pressure by funding bodies (NIH, NSF,
Europe, etc) to share data, it might be good to pretend (and only pretend) to be a
supporter of Open Data by inserting a simple ``data available upon request'' or
``data is available from my website''. This does not come close to meeting the
FAIR principles (findable, accessible, inter-operable, re-usable,
\cite{wilkinson:2016}), but who cares if you can give the illusion you're not
afraid of sharing your data? Don't get us wrong, though - you will never answer a
request, and the data will never appear on your website.

@@

Here comes the tricky part: replication. It may surprise you, but some researchers
may want to replicate your results using the methods explained in your
article. \citep{nosek:2015} replicated 100 experiments reported in three high-ranking psychology journal. Or tried, at least; they
concluded that some experiments were not replicable at all. There are even scientific journals that are now dedicated to replications
(e.g. \url{http://rescience.github.io}).

If people try to replicate your work
and do not get the same results, you have a problem. They may insist on seeing your actual
data and, if you refuse, you might be suspected of
fraud or misconduct. You can try rule 6, but if there are several failed replications, it will be much
harder to deny access to your data. One easy way to avoid this sort of disaster is
to claim in your article that the experiment/study has been already
replicated in your lab. The subliminal message to the reader is ``Don't bother
to replicate this, we've already taken care of that and it works, believe us. Don't
waste your time, you will thank us later''. If this doesn't work, you can also
try issuing a {\em Do Not Replicate order} as proposed by
\href{https://mchankins.wordpress.com/2014/07/12/do-not-replicate/}{Matthew
  Hankins} (who is kind enough as to provide a template). It is not yet widely
used , but with the replication crisis we're facing, we're confident it will soon become popular.

@@

If you've made a genuine (and big) mistake in your work, there is no problem in
asking for the retraction of your paper  \citep{miller:2006}. It's a
behavior that is actually rewarded according to \citep{lu:2013} (positive citation benefits for prior work), even though in some cases, it can take several years \citep{trivers:2009}. However, if you've been
engaged in fraud, having your paper retracted is like an admission of guilt. It's something to be avoided. Retraction could start with a simple comment to the
editor saying there may be a problem with you paper. If you're lucky, the comment will never be published
\citep{trebino:2009}. Otherwise, you'll have to give a convincing answer, or the editor could decide to retract your paper
without your consent. So it's critical to act quickly, defusing the crisis with a simple corrigendum admitting a bad - but not fatal - error during preparation of the publication.  Don't hesitate to publish as many corrigendum as
necessary to make critics happy. You can drag this out for several years, which is hopefully enough time for people to forget about the issues.

@@

If you look at the annual list of
\href{http://www.the-scientist.com/?articles.view/articleNo/47813/title/Top-10-Retractions-of-2016/}{top
  ten retractions} compiled by Adam Marcus and Ivan Oransky (co-founders of the
RetractionWatch), you'll realize that all the tactics mentioned above are
already quite well known by the research community. If you want to stay off the radar
while committing fraud and misconduct, you'll want to be creative and invent
your own rules.
